The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-15 manuscript.Rmd
[fix #23] get info for spp listed as "not in database"

Species that are included in the list but do not have records in databases could be (1) rare: they have never been collected or have been collected only a few times, and the corresponding records have not been digitized yet; (2) difficult to preserve: large, very small, or fragile species are preserved less frequently; (3) are in the database under a different name: the species has been synonimized or re-identified since the publication of the list under a different name that may be included in the database; (4) at the limit of its range: it was included in the list because it is known to occur at the limit of its geographic zone, but has never been collected within the boundaries; (5) does not have geographic coordinates associated with it: it can be in the database but without georeferenced datapoints that made it possible to discover them.

>>>>

Species that are included in the list but do not have records in databases could be (1) rare: they have never been collected or have been collected only a few times, and the corresponding records have not been digitized yet; (2) difficult to preserve: large, very small, or fragile species are preserved less frequently; (3) are in the database under a different name: the species has been synonimized or re-identified since the publication of the list under a different name that may be included in the database; (4) at the limit of its range: it was included in the list because it is known to occur at the limit of its geographic zone, but has never been collected within the boundaries; (5) does not have geographic coordinates associated with it: it can be in the database but without georeferenced datapoints that made it possible to discover them. By querying iDigBio we found that for the `r format(not_really_in_database$idig_gom_n_spp_not_in_db, big.mark=",")` species that do not appear within the geographic range of the Gulf of Mexico but are on the list, `r format_output(not_really_in_database$idig_gom_p_spp_not_in_db*100)`% are truly absent from iDigBio, while for the `r format(not_really_in_database$idig_gom_n_spp_no_coords, big.mark=",")` species that appear in iDigBio `r format_output(not_really_in_database$idig_gom_p_spp_no_coords*100)`%  do not have geographic coordinates associated with them, and for the ones that do `r format_output(not_really_in_database$idig_gom_p_spp_within_usa*100)`% fall within the US waters (n = `r format(not_really_in_database$idig_gom_n_spp_within_usa, big.mark=",")`).
